On the specific recursive structure of iterated parametricity

### 2025-11-10 paper/paper.tex
Another bunch of fixes/additions

Let us introduce another abbreviation to combine a full $\deps[n][0,n]$ with a family $E:\framep[n-1][n-1]\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][0,...,n-1] &:&\depstype[n][0,...,n-1] \\
            E&:&\frame[n-1][n-1](\deps[n][0,...,n-1]) \rightarrow \U         \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n][p]$ by recursion on $n-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]      &
    (\fulldeps[n-1]:\fulldepstype[n-1])           \\
    \painting[n][n]      &
    (\fulldeps[n-1])     & \defeq & \fulldeps.E   \\
    \painting[n][p](p<n) &
    (\fulldeps[n-1])     & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
              \painting[n][p+1,...,n-1]
              (\fulldeps[n-1])(d,l)                   \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

It is also convenient to abbreviate:

@@

\begin{align*}
  \overline{\fulldeps}(\fulldepscohs:\fulldepscohstype) & :      & \fulldepstype \\
  \overline{\fulldeps}(\fulldepscohs)               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}(\depscohs)\\
            \depscohs.\fulldeps.E\\
          \end{array}\right)             \\
\end{align*}

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
\begin{align*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{l}
            \depscohs[n][0,...,n-1] &:&\depscohstype[n][0,...,n-1]                         \\
            E&:&\framep[n-1][n-1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n][p]                           &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
        (\overline{\deps}(\depscohs)).    \\
        \painting[n][p]
        (\overline{\fulldeps}(\fulldepscohs[n])(d) \rightarrow \\
        \painting[n-1][p](\fulldepscohs.\depscohs.\fulldeps[n])
          (\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,n])(d))\end{array}\right)                                       \\
    \restrp[n][n]                           &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n][p](p<n)                      &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(l),               \\
              \restrp[n][p][q][\epsilon]
              (\fulldepscohs[n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
            \end{array}\right)                              \\
  \end{array}
\end{equation*}

@@

              \cohf[n][0,...,p][q][r][\epsilon][\omega]

@@

                \end{array}\right)(d)(l)                                     \\

@@

\begin{align*}
  \depscohttype[n][0,..,p-1] \defeq
  \left(\begin{array}{l}
            \fulldepscohs[n] :\fulldepscohstype[n]                        \\
            \cohp[n][0,...p-1]: \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
            \coht[n][0,...,p-1]: \cohttype[n][0,...,p-1]
            \left(\begin{array}{l}
                \fulldepscohs[n]    \\
                \cohp[n][0,...,p-1] \\
              \end{array}\right)                                     \\
          \end{array}\right)
\end{align*}

We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\overline{\deps}(\depscohs[n][0,...,n-1])))??? \rightarrow \U$:
\begin{align*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{l}
            \depscoht[n][0,...,n-1] :\depscohttype[n][0,...,n-1]    \\
            E:\framep[n-1][n-1](\overline{\deps}(??))\rightarrow \U \\
          \end{array}\right)
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohp[n][p]                                        &
    \left(\begin{array}{l}
              \depscoht[n][0,...,n]:\depscohttype[n][0,...,n] \\
              E:\framep[n-2][n-2]\rightarrow \U               \\
              E':\framep[n-1][n-1]\rightarrow \U              \\
              E'':\framep[n][n]\rightarrow \U                 \\
            \end{array}\right) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
        \depscohs.\restrp[n][p][q][\epsilon](\restrp[n+1][p][r][\omega]
        \left(\begin{array}{l}
                  \depscohs[n+1][0,...,n] \\
                  \cohp[n+1][0,...,p-1]   \\
                \end{array}\right)(d)) =                         \\
        \depscohs.\restrp[n][p][r][\omega](\restrp[n+1][p][q+1][\epsilon]
        \left(\begin{array}{l}
                  \depscohs[n+1][0,...,n] \\
                  \cohp[n+1][0,...,p-1]   \\
                \end{array}\right)(d))
      \end{array}\right)                                                                                                       \\
    \cohp[n][n]                                        &
    \left(\begin{array}{l}
              \depscoht[n][0,...,n] \\
              E                     \\
              E'                    \\
            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
    \cohp[n][p](p<n)                                   &
    \left(\begin{array}{l}
              \depscoht[n][0,...,n] \\
              E                     \\
              E'                    \\
            \end{array}\right)                           & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][\epsilon](\depscoht[n-1][0,...,p-1])(l),            \\
              \cohp[n][p][q][\epsilon]
              \left(\begin{array}{l}
                  \depscoht[n][0,...,n] \\
                  E                     \\
                  E'                    \\
                \end{array}\right)(\cohf[n][p](\depscoht[n][0,...,p])(d))(c) \\
            \end{array}\right)                                                                                         \\
  \end{array}
\end{equation*}

>>>>

Let us introduce another abbreviation to combine a full $\deps[n][0,n]$ with a family $E:\framep[n-1][n-1]\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][0,...,n-1] &:&\depstype[n][0,...,n-1] \\
            E&:&\frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U         \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n][p]$ by recursion on $n-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]      &
    (\fulldeps[n-1]:\fulldepstype[n-1])           \\
    \painting[n][n]      &
    (\fulldeps[n-1])     & \defeq & \fulldeps.E   \\
    \painting[n][p](p<n) &
    (\fulldeps[n-1])     & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
              \painting[n][p+1]
              (\fulldeps[n-1])(d,l)                   \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

It is also convenient to build $\deps$ from $\depscohs$ at the previous level:

@@

\begin{align*}
  \overline{\fulldeps}(\fulldepscohs:\fulldepscohstype) & :      & \fulldepstype \\
  \overline{\fulldeps}(\fulldepscohs)               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}(\fulldepscohs.\depscohs)\\
            \fulldepscohs.\depscohs.\fulldeps.E\\
          \end{array}\right)             \\
\end{align*}

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
\begin{align*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{l}
            \depscohs[n][0,...,n-1] &:&\depscohstype[n][0,...,n-1]                         \\
            E&:&\framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n][p]                           &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
        (\overline{\deps}(\depscohs)).    \\
        \painting[n][p]
        (\overline{\fulldeps}(\fulldepscohs[n])(d) \rightarrow \\
        \painting[n-1][p](\fulldepscohs.\depscohs.\fulldeps[n])
          (\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,n])(d))\end{array}\right)                                       \\
    \restrp[n][n]                           &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n][p](p<n)                      &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(...)(l),               \\
              \restrp[n][p][q][\epsilon]
              (\fulldepscohs[n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
            \end{array}\right)                              \\
  \end{array}
\end{equation*}

@@

              (\cohf[n][0,...,p][q][r][\epsilon][\omega]

@@

                \end{array}\right)(d)(l))                                     \\

@@

\begin{align*}
  \depscohttype[n][0,..,p-1] \defeq
  \left(\begin{array}{lll}
            \fulldepscohs[n] &:&\fulldepscohstype[n]                        \\
            \cohp[n][0,...p-1]&:& \cohptype[n][0,...,p-1](\fulldepscohs[n]) \\
            \coht[n][0,...,p-1]&:& \cohttype[n][0,...,p-1]
            \left(\begin{array}{l}
                \fulldepscohs[n]    \\
                \cohp[n][0,...,p-1] \\
              \end{array}\right)                                     \\
          \end{array}\right)
\end{align*}

It is also convenient to build $\depscohs$ from $\depscohtt$ at the previous level:

\begin{align*}
  \overline{\depscohs}(\depscoht:\depscohttype) & :      & \depscohstype \\
  \overline{\depscohs}(\depscoht)               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depcohs[n][0,...,p])   \\
            \restrpainting[n][p](\depscoht.\fulldepscohs[n][0,...,n]) \\
            \cohf[n][p](\depscoht[n][0,...,p])         \\
          \end{array}\right)             \\
\end{align*}

\begin{align*}
  \overline{\fulldepscohs}(\fulldepscoht:\fulldepscohstype) & :      & \fulldepscohstype \\
  \overline{\fulldepscohs}(\fulldepscoht)               & \defeq &
  \left(\begin{array}{l}
            \overline{\depscohs}(\fulldepscoht.\depscoht)\\
            \fulldepscoht.\depscoht.\fulldepscohs.E\\
          \end{array}\right)             \\
\end{align*}

We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\depscohs}(\depscoht[n][0,...,n-1])) \rightarrow \U$:
\begin{align*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{lll}
            \depscoht[n][0,...,n-1] &:&\depscohttype[n][0,...,n-1]    \\
            E&:&\framep[n+2][n+2](\overline{\depscohs}(\depscoht[n][0,...,n-1]))\rightarrow \U \\
          \end{array}\right)
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohp[n][p]                                        &
    (\fulldepscoht[n][0,...,n]:\fulldepscohttype[n][0,...,n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi c.\, \\
        \restrp[n][p][q][\epsilon](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][r][\omega]
        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c)) =                         \\
        \restrp[n][p][r][\omega](\overline{\fulldeps}(\depscoht))(\restrp[n+1][p][q+1][\epsilon]
        (\fulldepscoht.\depscoht.\fulldepscohs[n+1][0,...,n])(d)(c))                         \\
      \end{array}\right)                                                                                                       \\
    \cohp[n][n]                                        &
    (\fulldepscoht[n][0,...,n])
       & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
    \cohp[n][p](p<n)                                   &
    (\fulldepscoht[n][0,...,n])
       & \defeq & \lambda q\leq n.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][\epsilon](\fulldepscoht.\depscoht[n-1][0,...,p-1])(...)(l),            \\
              \cohp[n][p][q][\epsilon]
              (\fulldepscoht[n][0,...,n])(\cohf[n][p](\fulldepscoht.\depscoht[n][0,...,p])(d))(c) \\
            \end{array}\right)                                                                                         \\
  \end{array}
\end{equation*}
